An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-19 EconGrowthSeminar.Rnw
Fixed size of UK flag.
Added several additional flags. Added SSE vs. gamma graphs for all countries.

        \tiny
          \begin{tabular}{|c|c|c|}\hline
            $f$   & $\lambda$                & $m$\\
            \hline
            $k$   & \Sexpr{sfUSK["lambda"]}  & \Sexpr{sfUSK["m"]}\\
            \hline
            $l$   & \Sexpr{sfUSL["lambda"]}  & \Sexpr{sfUSL["m"]}\\
            \hline
            $q$   & \Sexpr{sfUSQ["lambda"]}  & \Sexpr{sfUSQ["m"]}\\
            \hline
            $x$   & \Sexpr{sfUSX["lambda"]}  & \Sexpr{sfUSX["m"]}\\
            \hline
            $u$   & \Sexpr{sfUSU["lambda"]}  & \Sexpr{sfUSU["m"]}\\
            \hline
          \end{tabular}
        \normalsize
      \end{center}
    \column{2.2in}
<<Results_Graph_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
createSFLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putat{figure_other/flag_us.pdf}{0.055}{2.14in}{1.59in}
\end{frame}

@@

\begin{frame}{Grid Search Over $\gamma$}{US Cobb-Douglas With $q$} %----------------------------
<<CDeGammaGraphsUS, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("US", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putat{figure_other/flag_us.pdf}{0.055}{2.14in}{1.59in}
\end{frame}

@@

        \tiny
          \begin{tabular}{|c|c|c|c|c|}\hline
            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
            \hline
                  & \Sexpr{cdUS["CD", "lambda"]} & \Sexpr{cdUS["CD", "alpha"]} & \Sexpr{cdUS["CD", "beta"]} & \Sexpr{cdUS["CD", "gamma"]}\\
            \hline
            $q$   & \Sexpr{cdqUS["CD", "lambda"]} & \Sexpr{cdxUS["CD", "alpha"]} & \Sexpr{cdqUS["CD", "beta"]} & \Sexpr{cdqUS["CD", "gamma"]}\\
            \hline
            $x$   & \Sexpr{cdxUS["CD", "lambda"]} & \Sexpr{cdxUS["CD", "alpha"]} & \Sexpr{cdxUS["CD", "beta"]} & \Sexpr{cdxUS["CD", "gamma"]}\\
            \hline
            $u$   & \Sexpr{cduUS["CD", "lambda"]} & \Sexpr{cduUS["CD", "alpha"]} & \Sexpr{cduUS["CD", "beta"]} & \Sexpr{cduUS["CD", "gamma"]}\\
            \hline
          \end{tabular}
        \normalsize
      \end{center}
    \column{2.2in}
<<Results_Graph_US_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
createCDLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putat{figure_other/flag_us.pdf}{0.055}{2.14in}{1.59in}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas With $q$} %----------------------------
<<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("UK", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putat{figure_other/flag_uk.png}{0.048}{2.14in}{1.59in}
\end{frame}

<<Coefs_ZA_CD>>=
cdZA <- cobbDouglasData("ZA")
cdqZA <- cobbDouglasData("ZA", "Q")
cdxZA <- cobbDouglasData("ZA", "X")
@
\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
  \begin{columns}[c]
    \column{2.2in}
      \begin{center}
        \cdeEqn
        \vspace{\baselineskip}

        \tiny
          \begin{tabular}{|c|c|c|c|c|}\hline
            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
            \hline
                  & \Sexpr{cdZA["CD", "lambda"]} & \Sexpr{cdZA["CD", "alpha"]} & \Sexpr{cdZA["CD", "beta"]} & \Sexpr{cdZA["CD", "gamma"]}\\
            \hline
            $q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{round(cdqZA["CD", "beta"], digits=4)} & \Sexpr{cdqZA["CD", "gamma"]}\\
            \hline
            $x$   & \Sexpr{cdxZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{round(cdxZA["CD", "beta"], digits=4)} & \Sexpr{cdxZA["CD", "gamma"]}\\
            \hline
          \end{tabular}
        \normalsize
      \end{center}
    \column{2.2in}
<<Results_Graph_US_ZA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
createCDLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putat{figure_other/flag_za.png}{0.055}{2.14in}{1.59in}
\end{frame}

>>>>

        \tiny
          \begin{tabular}{|c|c|c|}\hline
            $f$   & $\lambda$                & $m$\\
            \hline
            $k$   & \Sexpr{sfUSK["lambda"]}  & \Sexpr{sfUSK["m"]}\\
            \hline
            $l$   & \Sexpr{sfUSL["lambda"]}  & \Sexpr{sfUSL["m"]}\\
            \hline
            $q$   & \Sexpr{sfUSQ["lambda"]}  & \Sexpr{sfUSQ["m"]}\\
            \hline
            $x$   & \Sexpr{sfUSX["lambda"]}  & \Sexpr{sfUSX["m"]}\\
            \hline
            $u$   & \Sexpr{sfUSU["lambda"]}  & \Sexpr{sfUSU["m"]}\\
            \hline
          \end{tabular}
        \normalsize
      \end{center}
    \column{2.2in}
<<Results_Graph_US_SF, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
createSFLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putat{figure_other/flag_us.png}{0.055}{2.14in}{1.59in}
\end{frame}

@@

\begin{frame}{Grid Search Over $\gamma$}{US Cobb-Douglas With $q$} %----------------------------
<<CDeGammaGraphsUS, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("US", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putat{figure_other/flag_us.png}{0.055}{2.14in}{1.59in}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{UK Cobb-Douglas With $q$} %----------------------------
<<CDeGammaGraphsUK, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("UK", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putat{figure_other/flag_uk.png}{0.045}{2.14in}{1.59in}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{JP Cobb-Douglas With $q$} %----------------------------
<<CDeGammaGraphsJP, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("JP", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putat{figure_other/flag_jp.png}{0.045}{2.14in}{1.59in}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{CN Cobb-Douglas With $q$} %----------------------------
<<CDeGammaGraphsCN, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("CN", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putat{figure_other/flag_jp.png}{0.045}{2.14in}{1.59in}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{SA Cobb-Douglas With $q$} %----------------------------
<<CDeGammaGraphsSA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("SA", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putat{figure_other/flag_sa.png}{0.055}{2.14in}{1.59in}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{IR Cobb-Douglas With $q$} %----------------------------
<<CDeGammaGraphsIR, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("IR", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putat{figure_other/flag_ir.png}{0.055}{2.14in}{1.59in}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{ZM Cobb-Douglas With $q$} %----------------------------
<<CDeGammaGraphsZM, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph("ZM", "Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putat{figure_other/flag_zm.png}{0.055}{2.14in}{1.59in}
\end{frame}

@@

        \tiny
          \begin{tabular}{|c|c|c|c|c|}\hline
            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
            \hline
                  & \Sexpr{cdUS["CD", "lambda"]} & \Sexpr{cdUS["CD", "alpha"]} & \Sexpr{cdUS["CD", "beta"]} & \Sexpr{cdUS["CD", "gamma"]}\\
            \hline
            $q$   & \Sexpr{cdqUS["CD", "lambda"]} & \Sexpr{cdxUS["CD", "alpha"]} & \Sexpr{cdqUS["CD", "beta"]} & \Sexpr{cdqUS["CD", "gamma"]}\\
            \hline
            $x$   & \Sexpr{cdxUS["CD", "lambda"]} & \Sexpr{cdxUS["CD", "alpha"]} & \Sexpr{cdxUS["CD", "beta"]} & \Sexpr{cdxUS["CD", "gamma"]}\\
            \hline
            $u$   & \Sexpr{cduUS["CD", "lambda"]} & \Sexpr{cduUS["CD", "alpha"]} & \Sexpr{cduUS["CD", "beta"]} & \Sexpr{cduUS["CD", "gamma"]}\\
            \hline
          \end{tabular}
        \normalsize
      \end{center}
    \column{2.2in}
<<Results_Graph_US_CD, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
createCDLatticeGraph("US", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putat{figure_other/flag_us.png}{0.055}{2.14in}{1.59in}
\end{frame}

<<Coefs_ZA_CD>>=
cdZA <- cobbDouglasData("ZA")
cdqZA <- cobbDouglasData("ZA", "Q")
cdxZA <- cobbDouglasData("ZA", "X")
pprint <- function(num, digits = 4){
  out <- formatC(num, digit=digits, format="f")
  return(out)
}
@
\begin{frame}{Cobb-Douglas $y$ Predictions} %----------------------------
  \begin{columns}[c]
    \column{2.2in}
      \begin{center}
        \cdeEqn
        \vspace{\baselineskip}

        \tiny
          \begin{tabular}{|c|c|c|c|c|}\hline
            $e$ & $\lambda$ & $\alpha$ & $\beta$ & $\gamma$\\
            \hline
                  & \Sexpr{pprint(cdZA["CD", "lambda"])} & \Sexpr{cdZA["CD", "alpha"]} & \Sexpr{cdZA["CD", "beta"]} & \Sexpr{pprint(cdZA["CD", "gamma"])}\\
            \hline
            $q$   & \Sexpr{cdqZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{pprint(cdqZA["CD", "beta"])} & \Sexpr{cdqZA["CD", "gamma"]}\\
            \hline
            $x$   & \Sexpr{cdxZA["CD", "lambda"]} & \Sexpr{cdxZA["CD", "alpha"]} & \Sexpr{pprint(cdxZA["CD", "beta"])} & \Sexpr{cdxZA["CD", "gamma"]}\\
            \hline
          \end{tabular}
        \normalsize
      \end{center}
    \column{2.2in}
<<Results_Graph_US_ZA, fig.width=presentationGraph2ColWidth, fig.height=presentationGraph1RowHeight, fig.pos="H">>=
createCDLatticeGraph("ZA", textScaling=textScaleForGraphs, keyXLoc=keyXLoc, keyYLoc=keyYLoc)
@
  \end{columns}
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putat{figure_other/flag_za.png}{0.055}{2.14in}{1.59in}
\end{frame}
